\MakeUppercase{Layered $H$-Partitions of $k$-Planar Graphs} \thanks{This work was partly funded by NSERC and MRI.}

### 2019-05-13 k-planar.tex
langle and rangle for L

\begin{proof}
  We use the layered $H$-partition $(\mathcal{L}, \mathcal{S})$, where $\mathcal{S}=\{S_x:x\in V(K)\}$ and $\mathcal{L}=\{V_i': i=0,1,2\ldots\}$ where $V_i' = V_{(k+1)i}\cup\cdots\cup V_{(k+1)(i+1)-1}$.  \Eqref{distance-preserving} shows that $\mathcal{L}$ is indeed a layering of $G$.

@@

  Use the layering $\mathcal{L}=\{V_0',\ldots,V_h'\}$ where $V_i'=V_{2i}\cup V_{2i+1}$ for each $i\in\{0,\ldots,h\}$. That this is a layering of $G$ follows from \eqref{spar-distance}.  Since $|V_j\cap S_x|\le 15$ for every integer $i\ge 0$, $|V_i'\cap S_x|\le 30$ for every integer $i\ge 0$ and $x\in V(H)$.
\end{proof}

>>>>

\begin{proof}
  We use the layered $H$-partition $(\mathcal{L}, \mathcal{S})$, where $\mathcal{S}=\{S_x:x\in V(K)\}$ and $\mathcal{L}=\langle V_i': i=0,1,2\ldots\rangle$ where $V_i' = V_{(k+1)i}\cup\cdots\cup V_{(k+1)(i+1)-1}$.  \Eqref{distance-preserving} shows that $\mathcal{L}$ is indeed a layering of $G$.

@@

  Use the layering $\mathcal{L}=\langle V_0',\ldots,V_h'\rangle$ where $V_i'=V_{2i}\cup V_{2i+1}$ for each $i\in\{0,\ldots,h\}$. That this is a layering of $G$ follows from \eqref{spar-distance}.  Since $|V_j\cap S_x|\le 15$ for every integer $i\ge 0$, $|V_i'\cap S_x|\le 30$ for every integer $i\ge 0$ and $x\in V(H)$.
\end{proof}
